---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# IDConverter

<!-- badges: start -->
[![CRAN
status](https://www.r-pkg.org/badges/version/IDConverter)](https://cran.r-project.org/package=IDConverter)
[![Codecov test coverage](https://codecov.io/gh/ShixiangWang/IDConverter/branch/master/graph/badge.svg)](https://app.codecov.io/gh/ShixiangWang/IDConverter?branch=master)
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![](https://cranlogs.r-pkg.org/badges/grand-total/IDConverter?color=orange)](https://cran.r-project.org/package=IDConverter)
<!-- badges: end -->

The goal of IDConverter is to convert identifiers between biological databases.
Currently, I mainly use it for promoting cancer study.

## Installation

You can install the released version of IDConverter from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("IDConverter")
```

Or install the latest version of IDConverter in GitHub with:

``` r
remotes::install_github("ShixiangWang/IDConverter")
```

Or Gitee (better in China):

```r
remotes::install_git("https://gitee.com/ShixiangWang/IDConverter")
```

## Available features

ID convertions:

- `convert_custom()` - Convert custom database identifiers.
- `convert_icgc()` - Convert ICGC identifiers.
- `convert_pcawg()` - Convert PCAWG identifiers.
- `convert_tcga()` - Convert TCGA identifiers.
- `convert_hm_genes()` - Convert human/mouse gene IDs between Ensembl and Hugo Symbol system.

Others:

- `parse_gdc_file_uuid()` - Parse Metadata from GDC Portal File UUID.
- `filter_tcga_barcodes()` - Filter TCGA Replicate Sample Barcodes.

## Examples

```{r}
library(IDConverter)
```


### TCGA

```{r}
x <- convert_tcga("TCGA-02-0001-10")
x
```

### PCAWG

```{r}
x <- convert_pcawg("SP1677")
x
```

### ICGC

```{r}
x <- convert_icgc("SP29019")
x
```


## Citation

***Wang S, Li H, Song M, Tao Z, Wu T, He Z, et al. (2021) Copy
number signature analysis tool and its application in prostate
cancer reveals distinct mutational processes and clinical outcomes.
PLoS Genet 17(5): e1009557.***
<https://doi.org/10.1371/journal.pgen.1009557>

## Similar package

- [AnnoProbe](https://github.com/jmzeng1314/AnnoProbe/) ([Gitee mirror](https://gitee.com/jmzeng/annoprobe)) is an R package for transforming Chips probes to different Gene IDs.

## LICENSE

MIT\@2020, Shixiang Wang
