---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# IDConverter

<!-- badges: start -->
[![Lifecycle: stable](https://img.shields.io/badge/lifecycle-stable-brightgreen.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![](https://cranlogs.r-pkg.org/badges/grand-total/IDConverter?color=orange)](https://cran.r-project.org/package=IDConverter)
<!-- badges: end -->

The goal of IDConverter is to convert identifiers between biological databases.
Currently, I mainly use it for promoting cancer study.

## Installation

Install the latest version of IDConverter in GitHub with:

``` r
remotes::install_github("ShixiangWang/IDConverter")
```

Or Gitee (better in China, but not updated anymore):

```r
remotes::install_git("https://gitee.com/ShixiangWang/IDConverter")
```

## Available features

**ID conversions**:

- `convert_custom()` - Convert custom database identifiers.
- `convert_icgc()` - Convert ICGC identifiers.
- `convert_pcawg()` - Convert PCAWG identifiers.
- `convert_tcga()` - Convert TCGA identifiers.
- `convert_hm_genes()` - Convert human/mouse gene IDs between Ensembl and Hugo Symbol system.

Annotation tables from [annotables](https://github.com/stephenturner/annotables) are available
in this package, you can use `ls_annotables()` to print the table list and then use
`load_data()` to download and load the data into R for conversion operation.

**Others**:

- `parse_gdc_file_uuid()` - Parse Metadata from GDC Portal File UUID.
- `filter_tcga_barcodes()` - Filter TCGA Replicate Sample Barcodes.

## Examples

```{r}
library(IDConverter)
```

To follow the CRAN policy, I have to set `tempdir()` as default data path,
however, I recommend you set the data path to a specified path with
`options(IDConverter.datapath)`.

e.g.,

```{r}
options(IDConverter.datapath = system.file("extdata", package = "IDConverter"))
```

### TCGA

```{r}
x <- convert_tcga("TCGA-02-0001-10")
x
```

### PCAWG

```{r}
x <- convert_pcawg("SP1677")
x
```

### ICGC

```{r}
x <- convert_icgc("SP29019")
x
```

### Genes

```{r}
convert_hm_genes(c("TP53", "KRAS", "EGFR", "MYC"), type = "symbol")

# Or use data from annotables
ls_annotables()
grch37 = load_data("grch37")
head(grch37)
convert_custom(c("TP53", "KRAS", "EGFR", "MYC"),
               from = "symbol", to = "entrez", dt = grch37)
```


## Citation

***Wang S, Li H, Song M, Tao Z, Wu T, He Z, et al. (2021) Copy
number signature analysis tool and its application in prostate
cancer reveals distinct mutational processes and clinical outcomes.
PLoS Genet 17(5): e1009557.***
<https://doi.org/10.1371/journal.pgen.1009557>

## Similar package

- [AnnoProbe](https://github.com/jmzeng1314/AnnoProbe/) ([Gitee mirror](https://gitee.com/jmzeng/annoprobe)) is an R package for transforming Chips probes to different Gene IDs.

## LICENSE

MIT\@2020, Shixiang Wang
